### 2017-12-04 manuscript.rmd
updated tip names

  fix_names = function( tree ){
    # Apply changes to any tip names
    tree$tip.label = sub( '_', ' ', tree$tip.label ) # Change first underscore to space
    tree$tip.label = sub( 'sp_', 'sp', tree$tip.label ) # Fix trailing _ in Physonect sp_
    return( tree )
  }

@@

#Clean Raw Data
names(raw_data)[1] = "Species"
raw_data$Species = as.character(raw_data$Species)
raw_data$Species[which(raw_data$Species == "Kephyes")] = "Kephyes ovata"
raw_data$Species[which(raw_data$Species == "Lilyopsis")] = "Lilyopsis fluoracantha"
raw_data$Species[which(raw_data$Species == "Agalma")] = "Agalma elegans"
raw_data$Species[which(raw_data$Species == "Frillagalma")] = "Frillagalma vityazi"
raw_data$Species[which(raw_data$Species == "Stephalia")] = "Stephalia dilata"
raw_data$Species[which(raw_data$Species == "Lychnagalma")] = "Lychnagalma utricularia"
raw_data$Species[which(raw_data$Species == "Craseoa")] = "Craseoa lathetica"
raw_data$Species[which(raw_data$Species == "Cordagalma")] = "Cordagalma sp."
raw_data$Species[which(raw_data$Species == "Desmophyes haematogaster")] = "Desmophyes sp."
raw_data$Species[which(raw_data$Species == "Rudjakovia")] = "Rudjakovia sp."
raw_data$Species[which(raw_data$Species == "Thermopalia")] = "Stephalia sp." ##We should do something about this not corresponding...
raw_data$Species[which(raw_data$Species == "Physonectae sp. 1")] = "Undescribed Sp. L" #Is this correct?

@@

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```
```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
names(median_aggregate) = c("Spp","Depth")
median_aggregate[33,2] = 0
median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
median_depth = median_aggregate$Depth
names(median_depth) = median_aggregate$Spp
depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

>>>>

  gsub2 <- function(pattern, replacement, x, ...) {
  for(i in 1:length(pattern))
  x <- gsub(pattern[i], replacement[i], x, ...)
  x
  }

  correctnames =read.csv("tipcorrection.csv") #updating species IDs relative to agalma species IDs

  fix_names = function( tree ){
    # Apply changes to any tip names
    tree$tip.label = sub( '_', ' ', tree$tip.label ) # Change first underscore to space
    tree$tip.label = sub( 'sp_', 'sp', tree$tip.label ) # Fix trailing _ in Physonect sp_
    tree$tip.label = gsub2(correctnames$Agalma.ID, correctnames$Tree.ID,tree$tip.label)
    return( tree )
  }

@@

#Clean Raw Data
names(raw_data)[1] = "Species"
raw_data$Species = as.character(raw_data$Species)
raw_data$Species[which(raw_data$Species == "Kephyes")] = "Kephyes ovata"
raw_data$Species[which(raw_data$Species == "Lilyopsis")] = "Lilyopsis fluoracantha"
raw_data$Species[which(raw_data$Species == "Agalma")] = "Agalma elegans"
raw_data$Species[which(raw_data$Species == "Frillagalma")] = "Frillagalma vityazi"
raw_data$Species[which(raw_data$Species == "Stephalia")] = "Stephalia dilata"
raw_data$Species[which(raw_data$Species == "Lychnagalma")] = "Lychnagalma utricularia"
raw_data$Species[which(raw_data$Species == "Craseoa")] = "Craseoa lathetica"
raw_data$Species[which(raw_data$Species == "Cordagalma")] = "Cordagalma sp"
raw_data$Species[which(raw_data$Species == "Desmophyes haematogaster")] = "Desmophyes sp"
raw_data$Species[which(raw_data$Species == "Rudjakovia")] = "Rudjakovia sp"
raw_data$Species[which(raw_data$Species == "Physonectae sp. 1")] = "Undescribed sp L"

@@

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
names(median_aggregate) = c("Spp","Depth")
median_aggregate[33,2] = 0
median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
median_depth = median_aggregate$Depth
names(median_depth) = median_aggregate$Spp
depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```
